---
title: "dev_history.Rmd for working package"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
usethis::use_package("testhat")
usethis::use_package("rmarkdown")
usethis::use_package("devtools")
usethis::use_package("usethis")
usethis::use_package("tidyverse", type = "depends")
usethis::use_package("magrittr")
usethis::use_pipe()
library(testthat)
library(tidyverse)
library(rmarkdown)

```

<!--
# roascountries, member states of the OAS.

Returns a tibble with an iso3c column of all alpha 3 codes for OAS member states.
--> 

```{r description, eval=TRUE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "List of OAS member states country codes",
    Description = "A single get_oas_countries function that returns a tibble with the iso3c codes of OAS member states.",
    `Authors@R` = c(
      person("Alejandro", "Borges Sanchez", email = "alex@borges.consulting", role = c("aut", "cre")),
      person(given = "Alejandro Borges Sanchez", role = "cph")
    )
  ),
  overwrite = TRUE
)
# Define License with use_*_license()
usethis::use_mit_license("Alejandro Borges")
```

# Read data

<!-- Store your dataset in a directory named "inst/" at the root of your project -->
<!-- Use it for your tests in this Rmd thanks to `load_all()` to make it available
and `system.file()` to read it in your examples 
-->

```{r development-2}
# Run all in the console directly
# Create "inst/" directory
dir.create(here::here("inst"))
# Example dataset
# file.copy(system.file("nyc_squirrels_sample.csv", package = "fusen"), here::here("inst"))
# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)
# You will be able to read your example data file in each of your function examples and tests as follows
datafile <- system.file("oas_countries.csv", package = "roascountries")
oas_countries <- read.csv(datafile)
```


# Get OAS country codes as a tibble

```{r function}
#' Get OAS countries
#'
#'
#' @return
#' A dataset with one column iso3c
#' @export
#' 
#' @importFrom utils read.csv
#' @importFrom dplyr pull
#' @examples
#' get_oas_countries() %>% dplyr::pull(iso3c)
get_oas_countries <- function() {
  datafile <- system.file("oas_countries.csv", package = "roascountries")
  oas_countries <- read.csv(datafile)
  return(oas_countries)
}
```

```{r examples}
library(tidyverse)
get_oas_countries() %>% dplyr::pull(iso3c)
```

```{r tests}
oas_countries<-get_oas_countries()
test_that("It returns the correct dataset", {
  expect_true(nrow(oas_countries)==35,"number of rows is 35")
  expect_true(ncol(oas_countries)==1,"exactly one column")
  expect_true(names(oas_countries)=="iso3c")
  expect_true(all(c("MEX","VEN","ARG","USA") %in% oas_countries$iso3c),"Mexico, Venezuela, Argentina and USA are there")
})
```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
