---
title: "exploration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exploration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(roascountries)
```

<!--

# roascountries, member states of the OAS.

Returns a tibble with an iso3c column of all alpha 3 codes for OAS member states.
--> 


# Read data

<!-- Store your dataset in a directory named "inst/" at the root of your project -->
<!-- Use it for your tests in this Rmd thanks to `load_all()` to make it available
and `system.file()` to read it in your examples 
-->


# Get OAS country codes as a tibble

```{r examples}
library(tidyverse)
get_oas_countries() %>% dplyr::pull(iso3c)
```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory

